\bibitem{bib:DD4hep}  DD4Hep web page, http://aidasoft.web.cern.ch/DD4hep.

\bibitem{bib:LHCb} 		LHCb Collaboration, 
                "LHCb, the Large Hadron Collider beauty experiment, reoptimised detector 
				design and performance", CERN/LHCC 2003-030

\bibitem{bib:LHCb-geometry} S. Ponce et al., 
                "Detector Description Framework in LHCb", 
                International Conference on Computing in High Energy and Nuclear Physics  (CHEP 2003), 
                La Jolla, CA, 2003, proceedings. 

\bibitem{bib:ILD}  The ILD Concept Group, 
                   "The International Large Detector: Letter of Intent",\\
                   ISBN 978-3-935702-42-3, 2009.

\bibitem{bib:SiD}  H. Aihara, P. Burrows, M. Oreglia (Editors),
                   "SiD Letter of Intent",
                   arXiv:0911.0006, 2009.

\bibitem{bib:ROOT-tgeo} R.Brun, A.Gheata, M.Gheata, "The ROOT geometry package",\\
                    Nuclear Instruments and Methods {\bf{A}} 502 (2003) 676-680.

\bibitem{bib:ROOT} R.Brun et al., 
                   "Root - An object oriented data analysis framework",\\
                    Nuclear Instruments and Methods {\bf{A}} 389 (1997) 81-86.

\bibitem{bib:geant4}  S. Agostinelli et al., 
                   "Geant4 - A Simulation Toolkit", \\
                    Nuclear Instruments and Methods {\bf{A}} 506 (2003) 250-303.

\bibitem{bib:LCDD} T.Johnson et al., 
                   "LCGO - geometry description for ILC detectors", 
                   International Conference on Computing in High Energy and Nuclear Physics  (CHEP 2007), 
                   Victoria, BC, Canada, 2012, Proceedings.

\bibitem{bib:lcsim} N.Graf et al., 
                   "lcsim: An integrated detector simulation, 
                   reconstruction and analysis environment", 
                   International Conference on Computing in High Energy and Nuclear Physics (CHEP 2012),
                   New York, 2012, Proceedings.

\bibitem{bib:GDML} R. Chytracek et al.,
                   "Geometry Description Markup Language for Physics Simulation and Analysis
                   Applications",
                   IEEE Trans. Nucl. Sci., Vol. 53, Issue: 5, Part 2, 2892-2896,
                   http://gdml.web.cern.ch.
