%=============================================================================
\documentclass[10pt,a4paper]{article}
%
\input{./setup/DD4hep-setup.tex}
\input{./setup/AIDA2020-setup.tex}
%
\pagestyle{fancyplain}{\fancyfoot[C]{\sffamily{DDG4 User Manual}}}
%
\begin{document}   
%
\mytitle{DDG4}   % Abbreviated title
{  % Detailed title
A Simulation Toolkit for \\
\vspace{0.5cm}
High Energy Physics Experiments\\
\vspace{0.5cm}
using Geant4 and the \\
\vspace{0.5cm}
DD4hep Geometry Description\\
}
{  % Author list
M. Frank \\
{CERN, 1211 Geneva 23, Switzerland}
}
%
%
%==  Abstract  ===============================================================
\pagestyle{plain}
\pagenumbering{Roman}
\setcounter{page}{1}
\begin{abstract}
%=============================================================================

\noindent
\normalsize
Simulating the detector response is an essential tool in high energy physics
to analyze the sensitivity of an experiment to the underlying physics.
Such simulation tools require a detailed though convenient detector description as 
it is provided by the \DDhep toolkit.
We will present the generic simulation toolkit \DDG using the \DDhep detector 
description toolkit. 
The toolkit implements a modular and flexible approach to simulation activities
using Geant4. User defined simulation applications using \DDG 
can easily be configured, extended using specialized action routines.
The design is strongly driven by easy of use;
developers of detector descriptions and applications using
them should provide minimal information and minimal specific
code to achieve the desired result.

\end{abstract}

\vspace{10cm}

\begin{center}
{\large{\bf{
\begin{tabular} {| l | l | l |}
\hline
\multicolumn{3}{| c |}{} \\[0.2cm]
\multicolumn{3}{| c |}{Document History} \\[0.2cm]
\multicolumn{3}{| c |}{} \\[0.2cm]
\hline
                 &      &        \\
Document         &      &        \\
version          & Date & Author \\[0.2cm] \hline
                 &      &        \\
1.0              & 19/11/2013 & Markus Frank CERN/LHCb  \\
                 &      &        \\        \hline 
\end{tabular}
}}}
\end{center}

\clearpage
%
%
%==  TOC  ====================================================================
\tableofcontents
\clearpage
%
%
%=============================================================================
% Manual
%=============================================================================
\pagenumbering{arabic}
\setcounter{page}{1}
\graphicspath{{./figs/}}
\input{sections/Introduction.tex}
\input{sections/Implementation.tex}
\input{sections/Setup.tex}
\input{sections/HighLevel.tex}
\input{sections/MT.tex}
\input{sections/Components.tex}

%=============================================================================
\newpage
\begin{thebibliography}{9}
\input{Bibliography.tex}
\bibitem{bib:DDSegmentations} C.Grefe et al.,
                   "The DDSegmentation package", 
                   Non existing documentation to be written.
\bibitem{bib:Geant4-multi-threading} Geant4 Multi threading Guides. 
	Please see for details:\\
	https://twiki.cern.ch/twiki/bin/view/Geant4/Geant4MTAdvandedTopicsForApplicationDevelopers,\\
	https://twiki.cern.ch/twiki/bin/view/Geant4/QuickMigrationGuideForGeant4V10,\\
	http://geant4.slac.stanford.edu/tutorial/MC2015G4WS/Multithreading.pdf

\end{thebibliography}
%=============================================================================
\end{document}
